Part III

### 2021-06-04 PartI.tex
changes

\author{Owen Gwilliam and Brian R. Williams}
\date{\today}
%\title{Part I}

@@

\usepackage[upint]{stix}

\begin{document}
%\maketitle

@@

The mathematical motivation is simple:
for most holomorphic classical field theories, the solutions to the equations of motion form a moduli space of natural interest to complex geometers,
and it is natural to hope that its quantization is equally interesting.
A well-known example is holomorphic Chern-Simons theory,
which lives on a Calabi-Yau 3-fold $X$ and involves the {\em derived} moduli space $\RR\Bun_G(X)$ of holomorphic principal $G$-bundles on $X$.
As a somewhat mundane example, let $\RR\Hol(X,V)$ denote the derived moduli space of holomorphic maps from some complex manifold $X$ to another complex manifold $V$.
(For $V$ a vector space, a ``derived'' enhancement is familiar as the higher dimensional cohomology $H^*(X, \cO) \otimes V$.)
One can take a ``shifted cotangent bundle'' $T^*[-1] \RR\Hol(X,V)$,
and this derived moduli space encodes solutions to
a theory known as the $\beta\gamma$ system with target $V$.
(The name is silly: it's due to the original notation people used.)
Every question one asks about the classical physics of the $\beta\gamma$ theory translates into a question about this moduli space.

An essential example for us is ``holomorphic BF theory,''
which is a gauge theory for holomorphic principal $G$-bundles on a complex manifold $X$.
From the perspective of derived geometry, its solutions form the derived moduli space~$T^*[-1] \RR\Bun_G(X)$.

A physical motivation comes from supersymmetric field theories, 
which (loosely speaking) are theories on $\RR^n$ whose symmetries include not only the isometries of $\RR^n$, but an extension to a Lie supergroup known as a super Poincar\'e group.
The relevant extension is often labeled by $\cN=1, 2,$ and so on, 
with larger $\cN$ denoting a bigger supergroup. 
Thanks to the enhanced symmetry, such theories can often be understood in greater detail than non-supersymmetric theories.

For us, the crucial point is that supersymmetric theories admit ``twists'' (in essence, deformations) that are holomorphic field theories, 
even when they do not admit twists to TFTs (such as the famed A- and B-models of mirror symmetry) \cite{CosHol}.
As an example, $\cN=1$ supersymmetric Yang-Mills theory admits no topological twist, but does admit a twist to holomorphic field theory, namely a holomorphic BF theory.
It is natural to wonder how the myriad tools and computations deployed on the supersymmetric theory carry over to this twist and conversely whether information can flow back from a holomorphically twisted theory to the untwisted one, 
much as TFTs have enriched the understanding of supersymmetric theories.
In short, a holomorphic twist contains the ``holomorphic sector'' of the untwisted theory just as a topological twist contains its ``topological sector.''

@@

@@

Every supersymmetric field theory produces HFTs through a process called {\em twisting},
so we have a wealth of examples to study that are intimately connected to theories of genuine interest in physics.
As we will explain later, many interesting phenomena for supersymmetric theories have analogs for HFTs.

By definition, a supersymmetric field theory on $\RR^d$ is a theory that is acted upon by a super Poincar\'{e} algebra. 
In this paper we restrict our attention to Euclidean field theories and work in Riemannian signature,
hence for us the ``super Poincar\'{e} algebra'' is a super Lie algebra of the form
\[
\mathfrak{so}(d) \ltimes \ft
\]
where $\ft$ is the super Lie algebra of {\em supertranslations} whose even part $\ft^0 = \RR^d$ is the Lie algebra of ordinary translations and whose odd part $\ft^1$ is a sum of spin representations. 
While the Lie algebra $\RR^d$ of ordinary translations is abelian, the Lie algebra $\ft$ carries a nontrivial (super) Lie bracket,
and this Lie bracket is defined in terms of a $\mathfrak{so}(d)$-equivariant non-degenerate symmetric pairing
\[
\Gamma : {\rm Sym}^2(\ft^{1}) \to {\rm Sym}(\ft^0) \cong \RR^d 
\]
by the formula $[Q, Q'] = \Gamma(Q, Q')$.

@@

Building upon the physical literature, Elliott, Safronov, and the second author have given a complete characterization of the all twisted supersymmetric Yang--Mills theories in dimensions $2 \leq d \leq 10$ \autocite{ESW}. 
These twisted theories are analogs of BF theory and Chern--Simons theory,
exactly the kinds of theories we have already discussed, so long as one includes purely topological and purely holomorphic theories. 
We will describe a few examples in detail in the BV formalism in Section~\ref{sec:twistedsusybv},
but we want to indicate now what our main theorem implies about some interesting examples.

@@

>>>>

\author{Owen Gwilliam and Brian R. Williams}
\date{\today}
\title{Part I}

@@

%\usepackage[upint]{stix}

\begin{document}
\maketitle

@@

The mathematical motivation is simple:
for most classical holomorphic field theories, the solutions to the equations of motion form a moduli space of natural interest to complex geometers,
and it is natural to hope that its quantization is equally interesting.
A well-known example is holomorphic Chern-Simons theory,
which lives on a Calabi-Yau 3-fold $X$ and involves the {\em derived} moduli space $\RR\Bun_G(X)$ of holomorphic principal $G$-bundles on $X$.
Other classes of examples are afforded by holomorphic variants of familiar AKSZ $\sigma$-models; the relevant moduli space being the derived mapping space between complex manifolds.

A physical motivation comes from supersymmetric field theories, 
which (loosely speaking) are theories on $\RR^n$ whose symmetries include not only the isometries of $\RR^n$, but an extension to a Lie supergroup known as a super Poincar\'e group.
%The relevant extension is often labeled by $\cN=1, 2,$ and so on, 
%with larger $\cN$ denoting a bigger supergroup. 
Thanks to the enhanced symmetry, such theories can often be understood in greater detail than non-supersymmetric theories.
The relevance to the models we study is that supersymmetric theories admit ``twists'' (in essence, deformations) that are holomorphic field theories, 
even when they do not admit twists to TFTs (such as the famed A- and B-models of mirror symmetry) \cite{CosHol}.
As an example, four-dimensional minimally supersymmetric Yang-Mills theory admits no topological twist, but does admit a twist to holomorphic field theory whose moduli space is described, in part, by $\RR \Bun_G(X)$. 
It is natural to wonder how the myriad tools and computations deployed on the supersymmetric theory carry over to this twist and conversely whether information can flow back from a holomorphically twisted theory to the untwisted one, 
much as TFTs have enriched the understanding of supersymmetric theories.
In short, a holomorphic twist contains the ``holomorphic sector'' of the untwisted theory just as a topological twist contains its ``topological sector.''

@@

Let us begin with the example of holomorphic Chern--Simons theory, which we have already said describes the moduli space of

Maurer--Cartan elements describe deformations of the trivial holomorphic $G$-bundle. 
When $X$ is a Calabi--Yai three-fold, and $\fg$ is equipped with an invariant pairing, this formal moduli space has a very special property: it arises from the variational problem of an action functional, namely
\[
S = \int_X \Omega \wedge {\rm CS}(A) 
\]
where $\Omega$ is the holomorphic volume form and ${\rm CS}(A)$ is the Chern--Simons Lagrangian for the connection $(0,1)$-form $A$.

We turn to a formal definition underpinning the formal moduli spaces of the holomorphic field theories that we will be considering.

\begin{dfn}
A {\em holomorphic dg Lie algebra} on a complex manifold $X$ is the data:
\begin{itemize}
\item A graded holomorphic vector bundle $V$ on $X$ whose sheaf of holomorphic functions is $\cV^{hol}$. 
\item A holomorphic differential operator $Q^{hol} \colon \cV^{hol} \to \cV^{hol}$ of cohomological degree one and a holomorphic bidifferential operator $[\cdot,\cdot] \colon \cV^{hol} \times \cV^{hol} \to \cV^{hol}$. 
\end{itemize}
This data is required to endow $(\cV^{hol}, Q^{hol}, [\cdot,\cdot])$ with the structure of a dg Lie algebra.
\end{dfn}

Any holomorphic vector bundle has an associated Dolbeault complex $\Omega^{0,\bu}(X,V)$. 
If $V$ is a holomorphic dg Lie algebra then $\Omega^{0,\bu}(X, V)$ has the induced structure of a dg Lie algebra. 
The differential is of the form $\dbar + Q^{hol}$ and the bracket is given by extending the bracket on $\cV^{hol}$ with the wedge product of differential forms.

Formal moduli spaces arise from the space of Maurer--Cartan elements of a dg Lie algebra.
In our case, this dg Lie algebra will always be of the form $\Omega^{0,\bu}(X, V)$.
For example, the Maurer--Cartan elements of the dg Lie algebra $\Omega^{0,\bu}(X, \fg)$ recovers formal deformations of the trivial holomorphic $G$-bundle.  
This arises from the holomorphic Lie algebra on $X$ whose underlying vector bundle is trivial with fiber $\fg$.

As another example, consider the holomorphic tangent bundle $V = \T_X$. 
The Lie bracket of vector fields endows this with the structure of a holomorphic Lie algebra (with zero differential). 
A Maurer--Cartan element in $\Omega^{0,\bu}(X, \T_X)$ is an element $\mu \in \Omega^{0,1}(X, \T_X)$ satisfying the equation
\[
\dbar \mu + \frac12 [\mu,\mu] = 0 .
\]
This recovers the classical picture describing formal deformations of complex structures on~$X$.

@@

Any even dimensional supersymmetric field theory produces a holomorphic field theory through a process called twisting,
so we have a wealth of examples to study that are intimately connected to theories of genuine interest in physics.\footnote{Strictly speaking, this requires the existence of of more than two chiral supercharges. So, theories with 2d $\cN = (n,m)$ supersymmetry, $n,m \leq 1$, do not admit holomorphic twists.}
As we will explain later, many interesting phenomena for supersymmetric theories have analogs in holomorphic field theory.

By definition, a supersymmetric field theory on $\RR^d$ is a theory that is acted upon by a super Poincar\'{e} algebra. 
We focus on Euclidean field theories and work in Riemannian signature,
hence for us the ``super Poincar\'{e} algebra'' is a super Lie algebra of the form
$\mathfrak{so}(d) \ltimes \ft$
where $\ft$ is the super Lie algebra of {\em supertranslations} whose even part $\ft^0 = \RR^d$ is the Lie algebra of ordinary translations and whose odd part $\ft^1$ is a sum of spin representations. 
While the Lie algebra $\RR^d$ of ordinary translations is abelian, the Lie algebra $\ft$ carries a nontrivial (super) Lie bracket,
and this Lie bracket is defined in terms of a $\mathfrak{so}(d)$-equivariant non-degenerate symmetric pairing
\[
\Gamma : {\rm Sym}^2(\ft^{1}) \to {\rm Sym}(\ft^0) \cong \RR^d 
\]
by the formula $[Q, Q'] = \Gamma(Q, Q')$.

@@

Building upon the physical literature, Elliott, Safronov, and the second author have given a complete characterization of the all twisted supersymmetric Yang--Mills theories in dimensions $2 \leq d \leq 10$ \autocite{ESW}. 
These twisted theories are analogs of BF theory and Chern--Simons theory, so long as one includes purely topological and purely holomorphic theories. 
We will describe a few examples in detail in the BV formalism in Section~\ref{sec:twistedsusybv},
but we want to indicate now what our main theorem implies about some interesting examples.

@@

\subsection{More examples of holomorphic field theories}

\begin{itemize}
\item Target space field theories of topological string theories give rich classes of holomorphic field theories. 
For instance, the closed string field theory of the topological B-model is Kodaira--Spencer theory, first proposed in \cite{BCOV}. 
This theory is defined on any Calabi--Yau manifold. 
The perspective of Kodaira--Spencer theory as a holomorphic field theory has been explored with great success by Kevin Costello and Si Li \cite{CL1, CL2, CL3}.  
\item The `pure spinor' method of Cederwall and Berkovits \cite{Cederwall, Berkovits} starts with a field or string theory defined on the (sometimes singular) nilpotence variety of the super Poincar\'e algebra and uses the action of supersymmetry to produce ordinary (non-twisted) supersymmetric field theories. 
Often, the theory you start with on the nilpotence variety is holomorphic \cite{SWpure}. 
\item Similar in spirit to the pure spinor formalism is a systematic relationship between holomorphic field theories on (super) twistor space and ordinary (Riemannian) field theories.
For instance, holomorphic BF theory on twistor space associated to $\RR^4$ is equivalent to a self-dual limit of Yang--Mills theory. 
\end{itemize}

### 2021-06-04 PartIII.tex
changes

@@

>>>>

\subsection{Holomorphic factorization algebras}

We restrict ourselves to theories defined on complex affine space.
Let 
\beqn\label{eqn:affine}
\U(n) \ltimes \RR^{2n} \subset {\rm Aff}(\RR^{2n}) .
\eeqn
be the unitary affine group. 
A holomorphic factorization algebra on $\CC^n$ is a factorization algebra with an action by the unitary affine group where the anti-holomorphic translations act trivially (at least up to homotopy).

The (complexified) Lie algebra of \eqref{eqn:affine} is $\mathfrak{gl}(n) \ltimes \CC^{2n}$
with $\CC^{2n}$ spanned by the holomorphic and anti-holomorphic translations $\{\partial_{z_i}, \partial_{\zbar_i}\}$. 
A homotopical way to encode holomorphicity is to introduce the {\em dg} Lie algebra $\CC^{n}_{\rm hol}$ which in degree zero is the $2n$-dimensional space spanned by all translations $\{\partial_{z_i}, \partial_{\zbar_i}\}$, and in degree $(-1)$ is an $n$-dimensional space spanned by elements $\{\Bar{\eta}_i\}$. 
The differential is simply $\d \Bar{\eta}_i = \partial_{\zbar_i}$. 
Its immediate to see that $\CC^n_{\rm hol}$ is quasi-isomorphic to the abelian Lie algebra spanned by the {\em holomorphic} translations $\{\partial_{z_i}\}$.

\begin{dfn}
An $n$-dimensional {\em holomorphic factorization algebra} is a smoothly~\footnote{\brian{recall smooth}} affine equivariant factorization algebra $\cF$ on $\CC^n$ together with an extension of the complex Lie algebra of infinitesimal symmetries
to the dg Lie algebra $
\mathfrak{gl}(n) \ltimes \CC^{n}_{\rm hol}$. 
\end{dfn}

As an example, consider the `enveloping' type factorization algebra which is built out of the Dolbeault complex on $\CC^n$; it assigns to an open set $U \subset \CC^n$ the cochain complex
\[
{\rm Sym} \left(\Omega^{0,\bu}_c(U)\right) .
\]
This factorization algebra is clearly affine equivariant. 
Trivialization for the anti-holomorphic translation $\frac{\partial}{\partial \zbar_i}$ is given by the contraction of a Dolbeault form by the corresponding vector field:
\beqn\label{eqn:triv}
\Bar{\eta}_i = \frac{\partial}{\partial \zbar_i} \vee (-).
\eeqn

@@

From a geometric perspective, holomorphic $\sigma$-models form an extremely natural class of holomorphic field theories defined in arbitrary complex dimensions.

We turn our attention to the holomorphic $\sigma$-model of maps $\CC^n$ to the $(n-1)$-shifted cotangent bundle $\T^*[n-1] Y$ of a complex manifold $X$. 
Being a holomorphic AKSZ model, this theory a priori depends on the holomorphic volume form on $\CC^n$; but there is a 
\brian{not sure if this is discussed elsewhere}
\[
{\rm Map}(\CC^n, \T^*[n-1] X) \simeq \T^*[-1] {\rm Map}(\CC^n, X) .
\]
